%-----------PROJECTS-----------%
\section{Projects}
\resumeSubHeadingListStart

    \resumeProjectHeading
    {\textbf{MPU Tester} $|$ \href{https://github.com/adityakhode/MPUTESTER/}{ \textcolor{blue}{\textit{Github Link}}}  $|$
    \href{https://www.youtube.com/watch?v=Y0fbIhlIZoM\&list=PLDbTtMby4HbyvxpOV6Lv6e-EuP07iU_90}{ \textcolor{blue}{\textit{Youtube Link}}}} {}
    \resumeItemListStart
        \resumeItem {Built a desktop GUI application using \textbf{PySide6} for testing Magnetic Pickup Units (MPUs) on \textbf{Ubuntu Linux systems}.}
        \resumeItem{Integrated serial communication via pyserial for real-time sensor data acquisition from MPU hardware.}
        \resumeItem{Automated QR code and certificate generation using qrcode and Pillow, enhancing traceability and documentation.}
        \resumeItem{Designed a modular architecture with \textbf{ SQLite-based local database} for managing test results, units, and party metadata.}
        \resumeItem{Enabled certificate printing through \textbf{Linux CUPS}, optimized for low-power environments including Raspberry Pi devices.}
        \resumeItem{Reduced manual work by \textbf{85 percent}.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Qt-based karaoke application} $|$
    \href{https://www.youtube.com/watch?v=y99DjyUAuT4\&list=PLDbTtMby4HbyvxpOV6Lv6e-EuP07iU_90\&index=3}{ \textcolor{blue}{\textit{Youtube Link}}}} {}

    \resumeItemListStart
        \resumeItem{Developed a Qt-based karaoke application for Linux that performs real-time audio stem separation using pre-trained models like Demucs and Spleeter.}
        \resumeItem{Implemented user-selectable source separation models to split audio into vocals, drums, bass, and instruments, with independent volume control for each stem.}
        \resumeItem{Added features for tempo and pitch adjustment, enhancing user interactivity and customization of audio playback.}
        \resumeItem{Integrated drag-and-drop file handling, playback controls, and export functionality supporting multiple audio formats.}
        \resumeItem{Enabled seamless workflow with Audacity for advanced editing, and optimized the application for resource-constrained environments.}
    \resumeItemListEnd

     \resumeProjectHeading
    {\textbf{Luminosity Drone} $|$ \href{https://www.youtube.com/watch?v=44H_h2GXX0w\&list=PLDbTtMby4HbyvxpOV6Lv6e-EuP07iU_90\&index=4}{ \textcolor{blue}{\textit{Youtube Link}}}} {}
    \resumeItemListStart
        \resumeItem{Led a team in developing an autonomous drone system capable of navigating and capturing thermal images of LED arrays for pattern detection.}
        \resumeItem{Implemented image processing algorithms in Python to analyze thermal data and identify LED activation patterns in real time.}
        \resumeItem{Utilized ROS (Robot Operating System) for modular control, sensor integration, and autonomous flight path planning.}
        \resumeItem{Designed and tested the system in resource-constrained environments, ensuring reliable performance in dynamic conditions.}
        \resumeItem{Coordinated team efforts across hardware integration, software development, and testing phases, delivering a fully functional prototype.}
    \resumeItemListEnd

   

\resumeSubHeadingListEnd


